---
title: "Model overview"
author: "Michael Schirmer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Model overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Hydrological models

Hydrological models included and tested in the openQUARREL package.

**Note:** There are more models in the original packages, e.g. daily and monthly models in airGR or redundant airGR models in the hydromad package.

```{r, echo=FALSE}

knitr::kable(
  tibble::tibble(
    Model = c(
      "GR4J", "GR5J", "GR6J",
      "CemaNeigeGR4J", "CemaNeigeGR5J", "CemaNeigeGR6J",
      "cmd", "snow", "cwi", "awbm", "sacramento", "bucket",
      "TUW",
      "topmodel"
    ),
    "has own snow module" = c(
      "", "", "", 
      "X", "X", "X",
      "", "X", "", "", "", "",
      "X",
      ""
    ),
    Package = c(
      rep("[airGR](https://hydrogr.github.io/airGR/index.html)", 6),
      rep("[hydromad](https://hydromad.github.io/index.html)", 6),
      "[TUWmodel](https://rdrr.io/cran/TUWmodel/man/TUWmodel.html)",
      "[topmodel](https://github.com/ICHydro/topmodel) "
    )
  ),
  align = c("l", "c", "l")
)

```



## Snow modules

Snow modules included and tested in the openQUARREL package. TUWsnow is the snow module of TUWmodel. The snow module of snow is not separately implemented yet.

```{r, echo=FALSE}

knitr::kable(
  tibble::tibble(
    "Snow module" = c(
      "CemaNeige", "TUWsnow"
    ),
    Package = c(
      "airGR", "TUWmodel"
    )
  ),
)

```
