---
title: "Run a hydrological model (minimalistic example)"
author: "Michael Schirmer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Run a hydrological model (minimalistic example)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette shows how to run a hydrological model as a minimalistic example.

## Preparations

Load packages

```{r packages, include=FALSE}
library(openQUARREL)
library(dplyr)
```

```{r packages_showcode, eval=FALSE}
library(openQUARREL)
library(dplyr)
```


Create a minimum input
```{r minimum data}
# input_data is an example input loaded with openQUARREL
minimum_input <- input_data %>% 
  # filter to a single catchment, i.e. Thur at Jonschwil
  filter(HSU_ID == "2303") %>% 
  # select only a few columns
  select(DatesR, P, T, E)

# convert Date to POSIXct
minimum_input$DatesR <- as.POSIXct(minimum_input$DatesR)
attr(minimum_input$DatesR, "tzone") <- "UTC"
```

The data frame `minimum_input` contains columns `P` for precipitation in mm/d, `T` for air temperature in degrees Celsius and `E` for potential evapotranspiration in mm/d. See also the great [airGR get started](https://hydrogr.github.io/airGR/page_1_get_started.html) documentation. If you need to calculate `E`, there are functions available, e.g. in [airGR::PE_Oudin](https://rdrr.io/cran/airGR/man/PE_Oudin.html).

```{r show_table, echo=FALSE}
knitr::kable(head(minimum_input))
```

Choose a hydrological model
```{r settings}
# default_cal_par are default calibration parameter loaded with openQUARREL
# todo: cal_par needs to be a global parameter currently, needs to be changed in future releases
cal_par <- default_cal_par 
# todo: topmodel is not running right now as the required BasinInfo is not provided in example data
model <- "TUW"
```

### Set model parameters

Create a parameter set, which is here the middle points of the provided intervals. See [TUWmodel](https://rdrr.io/cran/TUWmodel/man/TUWmodel.html) documentation for parameter explanation. The list `default_cal_par` is loaded with `library(openQUARREL)` and holds model and calibration specific settings. 
```{r param}
param <- (cal_par[[model]]$upper + default_cal_par[[model]]$lower) / 2
print(param)
```

### Create input

This is done specifically for each model/package requirement, here [TUWmodel](https://rdrr.io/cran/TUWmodel/man/TUWmodel.html).
```{r input}
# todo: the last input can be empty, will be not required in a future release 
input <- create_input(model, minimum_input, list())
```


## Run the model
```{r run_model}
sim <- simulate_model(model, param, input)
```

The output is a list with fields `r names(sim)`. You can access typical components as simulated discharge `Qsim`, and if provided in the input also the observed discharge `Qobs`. If a snow module is integrated in the model or chosen to be added (see `vignette("include_snow_module")`) snow water equivalent `SWE`, the partitioned precipitation fluxes `pliquid` and `psolid`, and the snow `melt` flux. The element `more_info` is specific to the chosen model and package, in this case [TUWmodel](https://rdrr.io/cran/TUWmodel/man/TUWmodel.html).  
```{r output}
str(sim)
```

## Plot results
Here is a simple plot for simulated discharge with skipping the first ~3 years (warm-up):
```{r plot}
plot(sim$date[3*365:length(sim$date)], sim$Qsim[3*365:length(sim$date)], type = "l", main = "Simulated Discharge", ylab = "Q [mm/d]", xlab = "Date")

```

## Next steps
Now you do this again with a different hydrological model (see table in `vignette("model_overview")`), or proceed with `vignette("include_snow_module")`. 
